Declarative Data Analytic

### 2015-07-02 paper.tex
Meeting log for 7/1

\usepackage{cite}
\usepackage{url}

@@

Within the framework, we have a library which stores behavior
models (i.e., causal relationship). There will also be a root cause analysis
engine that is responsible
for generating the root cause based on the anomaly, the logs and the
library. A possible design for the root cause analysis engine
could be first to find the behavior models that have the anomaly as root---These
models are called failure models for the anomaly---then the
engine finds all log sequences satisfying the behavior model (we can
leverage \saf{} for this part), and runs the root cause analysis algorithm on
the log sequences found.

The behavior library needs to be specified by the user---it is almost impossible
to infer the behavior models without human input---and a language is needed for
the user to specify, manipulate, and query the library. The language could be any
existing language, such as \saf{} and Datalog, or a newly designed one.

@@

@@

>>>>

\usepackage{cite}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{color}

@@

Within the framework, we have a library which stores behavior
models (i.e., causal relationship). There will also be a root cause analysis
engine that is responsible
for generating the root cause based on the anomaly, the logs and the
library. 
(\textcolor{red}{Root cause analysis engine is only used for case study.6/24}) 
\sout{A possible design for the root cause analysis engine
could be first to find the behavior models that have the anomaly as root---These
models are called failure models for the anomaly---then the
engine finds all log sequences satisfying the behavior model (we can
leverage \saf{} for this part), and runs the root cause analysis algorithm on
the log sequences found. }

The behavior library needs to be specified by the user (\textcolor{red}{or the
  domain-specific expert. 6/25}) ---it is almost impossible
to infer the behavior models without human input---and a language is needed for
the user to specify, manipulate, and query the library. \sout{The language could be any
existing language, such as \saf{} and Datalog, or a newly designed one.}

@@

\paragraph{6/24}

In today's meeting, I gave a survey on three commercial solutions for root
cause analysis through log
analytics---namely HP solution, CA technology solution and IBM solution. Among
the three solutions, HP solution provides guidance on the work flow
for root cause analysis. CA technology is similar to SAF, and their event rule
idea is helpful in our project. IBM solution, however, is closer to a
search-filter analytic tool, which allows the administrator to plot different
statistical graphs based on the logs. More details can be found on the slides
for the weekly meeting on June 24.

The design of the declarative language for our project was further discussed in
the meeting. The language should extend the design of SAF. In SAF, a behavior is merely
a set of events. This is not enough for a complex and heterogeneous computing
environment. In such an environment, users' knowledge of the system could vary among different
levels. For example, a domain-specific expert could be more familiar with a
certain types of devices, such as database servers or email servers, while a
network administrator could know more about the protocol-level information along with
topological information. Our language should provide the opportunity for
different users to specify their specific knowledge of the system, and manages these
knowledge effectively in the storage, so that root cause analysis can be
performed with these knowledge.

\paragraph{To-do}

\begin{itemize}
\item Detailed work flow of the user.
\item Connect SAF with ElasticSearch: decouple SAF from SQLite, and use restful
  api as the query language.
\item Survey on languages that allow the user to specify causality relationship
  on different granularity.
A: Ontology is an interesting concept. 
\end{itemize}

\paragraph{7/1}

In today's meeting, we clarify the work flow of performing root cause analysis
in a typical network, and the problem to be targeted at during my summer
internship. Additionally, we discussed about the next few steps of the project
towards our goal.

\begin{itemize}
\item {\bf Word flow.} The work flow of the root cause analysis is as follows:
  \begin{itemize}
  \item The user reports an abnormal symptoms to the network administrator. The
  abnormal symptoms include high latency or no response of a specific
  service. The user usually specify such symptoms informally, such as in natural
  languages.
  \item Next, the network administrator would start the root cause analysis by
  collecting log traces from all the devices in the network. Since devices could
  be manufactured by different vendors, the logs could be in a variety of forms.
  \item To allow for computer-aided log analysis, the network administrator should
  be able to convert logs of different formats into a unified one
  (e.g. relational database).
  \item With the unified log database, the network administrator should be
  able to specify the symptoms reported by the user rigorously. A failure symptom
  could be formally defined as a set of database entries, or events. 
  \item In addition to the symptom specification and the log traces, the network
  administrator still needs network provenance (i.e., dependency relationship
  between events or set of events) to help identify the root cause
  analysis. In the usual scenario of log analytics, the network provenance is not
  given beforehand. The network administrator needs to infer the provenance
  information based on his domain-specific knowledge, such as topological
  layout.
  \item The network administrator would then run the root cause analysis algorithm
  based on the given symptom and the provenance information to identify the root
  cause of the system anomaly. 
  \end{itemize}

\item {\bf Targeted problem.}
  The targeted problem scope of our project is the part of provenance knowledge
  maintenance. It is assumed that the log has been organized into a uniform format
  (e.g., relational database), and basic database queries are available (e.g.,
  through SQL language). The goal is to have a framework that allows the user to
  specify, query, validate and operate on semantic provenance --- The semantic level could
  be flexible \textcolor{red}{more clear on what semantic level means}.

  There are several requirements worth considering:
  \begin{itemize}
  \item The framework should be able to map the specified semantic provenance to
    corresponding low-level semantics, where the lowest-level semantics is the
    log traces.

  \item The knowledge base should have categorization. For example, topological
    knowledge should be differentiated from protocol knowledge. Protocol
    knowledge could be reused across systems, but topological knowledge cannot.

  \item 
  \end{itemize}

@@

\item Root cause analysis in market products:

  \begin{itemize}
  \item The 4 Building Blocks of Root Cause Analysis
    (\url{http://apmdigest.com/the-4-building-blocks-of-root-cause-analysis}): The
    best practice is to unify the three layers into a single infrastructure
    management dashboard, so you can visually correlate all three levels of
    analytics in an efficient workflow.
  \item HP Operations Analytics (\url{https://www.youtube.com/watch?v=d3_r9-tFISk})
  \item Hui Zhang's email (6/15)
  \end{itemize}

\item Knowledge Discovery in Databases: An Overview 
(\url{https://mitpress.mit.edu/sites/default/files/titles/content/9780262660709_sch_0001.pdf})

\item Semantic Data Access to Relational Databases: IBM research
(\url{http://www.w3.org/wiki/images/9/90/Rdb2RdfXG$SeDA2RDB2RDFXG.pdf})
